--- 
title: "附录"
# subtitle: "Lecture title"
author:
- affiliation: Dongbei University of Finance & Economics
  name: Studennt. Li Junjie
date: '`r Sys.Date()`'
output:
  bookdown::html_document2:
    # code_folding: hide
    highlight: pygments
    # highlight: zenburn
    # highlight: haddock
    theme: darkly
    # theme: flatly
    df_print: paged	
    number_sections: true
    keep_md: no
    keep_tex: no
    toc: yes
    toc_depth: 5
    toc_float:
      collapsed: no
      smooth_scroll: yes
    # css: styles.css
# bibliography: [book.bib, packages.bib]
# biblio-style: apalike
link-citations: yes
sansfont: Times New Roman
always_allow_html: yes
urlcolor: "red"
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
abstract: |
    本章介绍 R 语言编程与数据可视化基础，对比了 base、 lattice 和 ggplot2 包的图形语法，重点介绍了 ggplot2 包的图形语法介绍 R 语言编程与数据可视化基础，对比了 base、 lattice 和 ggplot2 包的图形语法，重点介绍了 ggplot2 包的图形语法
    
    源代码下载 Github 网址： <https://github.com/EasyChart/Beautiful-Visualization-with-R>
---

# 加载经常用的R包

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      cache = FALSE,
                      fig.show = "hold",
                      fig.align = "center",
                      tidy = FALSE)
                      # class.source = "bg-warning")
```

```{r,echo=FALSE}
library(bubblyr)
bubblyr::bubbly(theme = "sweet")
# bubblyr::bubbly(theme = "rladies")
```

```{js, echo=FALSE}
$('.title').css('color', 'red')
$('.title').css('font-family', 'Times New Roman')
```

```{css, echo=FALSE}
* {
    # font-size: 17px !important;
    font-family: "Times New Roman" !important;
    # color: rgb(199 237	204)
}

code {
    font-size: 18px !important;
    font-family: "Times New Roman" !important;
    # color: rgb(199 237	204)
}
::selection {
   # background: rgb(135 206 255);
}
```

# The shell

## What is the shell?

## Starting the shell

## Windows is special … and not in a good way

## Basic shell commands

- `pwd` (print working directory). Shows directory or “folder” you are currently operating in. This is not necessarily the same as the R working directory you get from getwd().
- `ls` (list files). Shows the files in the current working directory. This is equivalent to looking at the files in your `Finder/Explorer/File Manager`. Use ls `-a` to also list hidden files, such as .Rhistory and .git.
- `cd` (change directory). Allows you to navigate through your directories by changing the shell’s working directory. You can navigate like so:
  - go to subdirectory foo of current working directory: `cd foo`
  - go to parent of current working directory: `cd ..`
  - go to your “home” directory: `cd ~` or simply `cd`
    - `Pro tip 1`: Dragging and dropping a file or folder into the terminal window will paste the absolute path into the window.
    - `Pro tip 2`: Use the tab key to auto complete unambiguous directory and file names. Hit tab twice to see all ambiguous options.
- Use `arrow-up` and `arrow-down` to repeat previous commands. Or search for previous commands with CTRL + r.

A few Git commands:

- `git status` is the most used git command and informs you of your current branch, any changes or untracked files, and whether you are in sync with your remotes.
- `git remote -v` lists all remotes. Very useful for making sure git knows about your remote and that the remote address is correct.
- `git remote add origin GITHUB_URL` adds the remote GITHUB_URL with nickname origin.
- `git remote set-url origin GITHUB_URL` changes the remote url of origin to GITHUB_URL. This way you can fix typos in the remote url.
- Feel free to suggest other commands that deserve listing in a GitHub issue.




















































